---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# mallaRd

<!-- badges: start -->
<!-- badges: end -->

The goal of mallaRd is to reproduces the analyses and results from the paper "Housing search in the concrete jungle – breeding site selection of urban mallards and implications for conservation management strategies" by Engler et al. (in prep). 

## Installation and usage

You can install our package mallaRd from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
install.packages("remotes") ## install the package remotes if you don't have it
remotes::install_github("courtiol/mallaRd") ## install our package
```

Then load the package in your R session and check the main help page where we placed all analyses:

```{r, eval=FALSE}
load("mallaRd")
?mallaRd
```

## Developer corner

Here is the information of the environment we used to run all the analyses:

```{r, eval=TRUE}
sessionInfo()
```

