---
output:
  github_document:
    df_print: kable
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(mallaRd)
```


# mallaRd

<!-- badges: start -->
<!-- badges: end -->

The goal of mallaRd is to reproduces the analyses and results from the paper "Housing search in the concrete jungle – breeding site selection of urban mallards and implications for conservation management strategies" by Engler et al. (in prep). 

## Installation and usage

You can install our package mallaRd from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
install.packages("remotes") ## install the package remotes if you don't have it
remotes::install_github("courtiol/mallaRd") ## install our package
```

Then load the package in your R session and check the main help page where we placed all analyses:

```{r, eval=FALSE}
load("mallaRd")
?mallaRd
```

## Raw data

You can access the raw data used for the paper [here](inst/extdata/raw_data.csv) or via the R package:

```{r, eval=TRUE}
head(data_raw) ## first 6 rows
```

## Developer corner

Our package relies on the following packages:

```{r, eval=TRUE}
pkgs <- desc::desc_get_deps()
pkgs <- pkgs[pkgs$package!="R", ]
pkgs$version_used <- sapply(pkgs$package, \(pkg) paste(packageVersion(pkg), sep = "."))
pkgs
```

Here is the information of the R & RStudio environment used to run all the analyses:

```{r, eval=TRUE}
sessionInfo()
```

